Fine-scale Data Reveals Neighborhood Inequalities In Effects of Heat on Expressed Mood

### 2021-07-01 doc/temp-sentiment.tex
submitted versions of files

\author[1,*]{Matthew Cooper}
\author[2]{Jeremiah Osborne-Gowey}
\author[3]{Zheng Liu}
\author[4]{Portia Adade Williams}
\author[5]{Jie Liu}
\author[6]{Aaron Schwartz}
\author[7]{Patrick Baylis}

\affil[1]{T.H. Chan School of Public Health, Harvard University}
\affil[2]{Environmental Studies Program, University of Colorado Boulder}
\affil[3]{Department of Geographical Sciences, University of Maryland College Park}
\affil[4]{CSIR-Science and Technology Policy Research Institute, Ghana}
\affil[5]{School of Business, East China University of Science and Technology}
\affil[6]{University of Colorado Boulder}
\affil[7]{University of British Columbia}
\affil[*]{Corresponding Author: mcooper@hsph.harvard.edu}

@@

%\printbibliography
\bibliography{TextDataClimateShocks}

\section*{Author Contributions}
Author contributions: M.C., J.O.-G., A.S. and P.B. designed the research and modeling strategy; A.S. provided data; M.C and Z.L. prepared data; M.C. and J.O.-G. analyzed data; and M.C., J.O.-G., P.A.W., and J.L. wrote the paper.

>>>>

\author{}
% \author[1,*]{Matthew Cooper}
% \author[2]{Jeremiah Osborne-Gowey}
% \author[3]{Zheng Liu}
% \author[4]{Portia Adade Williams}
% \author[5]{Jie Liu}
% \author[6]{Aaron Schwartz}
% \author[7]{Patrick Baylis} 
% 
% \affil[1]{T.H. Chan School of Public Health, Harvard University, U.S.A.}
% \affil[2]{Environmental Studies Program, University of Colorado Boulder, U.S.A.}
% \affil[3]{Department of Geographical Sciences, University of Maryland College Park, U.S.A.}
% \affil[4]{CSIR-Science and Technology Policy Research Institute, Ghana}
% \affil[5]{School of Business, East China University of Science and Technology, China} 
% \affil[6]{Department of Ecology \& Evolutionary Biology, University of Colorado Boulder, U.S.A.}
% \affil[7]{Vancouver School of Economics, University of British Columbia, Canada}
% \affil[*]{Corresponding Author: mcooper@hsph.harvard.edu}

@@

%\bibliography{TextDataClimateShocks}

\begin{thebibliography}{10}
\urlstyle{rm}
\expandafter\ifx\csname url\endcsname\relax
  \def\url#1{\texttt{#1}}\fi
\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
\expandafter\ifx\csname doiprefix\endcsname\relax\def\doiprefix{DOI: }\fi
\providecommand{\bibinfo}[2]{#2}
\providecommand{\eprint}[2][]{\url{#2}}

\bibitem{pachauri2014climate}
\bibinfo{author}{Pachauri, R.~K.} \emph{et~al.}
\newblock \emph{\bibinfo{title}{Climate change 2014: synthesis report.
  Contribution of Working Groups I, II and III to the fifth assessment report
  of the Intergovernmental Panel on Climate Change}}
  (\bibinfo{publisher}{Ipcc}, \bibinfo{year}{2014}).

\bibitem{Berry2018Apr}
\bibinfo{author}{Berry, H.~L.}, \bibinfo{author}{Waite, T.~D.},
  \bibinfo{author}{Dear, K. B.~G.}, \bibinfo{author}{Capon, A.~G.} \&
  \bibinfo{author}{Murray, V.}
\newblock \bibinfo{journal}{\bibinfo{title}{{The case for systems thinking
  about climate change and mental health}}}.
\newblock {\emph{\JournalTitle{Nat. Clim. Change}}}
  \textbf{\bibinfo{volume}{8}}, \bibinfo{pages}{282--290},
  \doiprefix\url{10.1038/s41558-018-0102-4} (\bibinfo{year}{2018}).

\bibitem{Collins2011Jul}
\bibinfo{author}{Collins, P.~Y.} \emph{et~al.}
\newblock \bibinfo{journal}{\bibinfo{title}{{Grand challenges in global mental
  health}}}.
\newblock {\emph{\JournalTitle{Nature}}} \textbf{\bibinfo{volume}{475}},
  \bibinfo{pages}{27--30}, \doiprefix\url{10.1038/475027a}
  (\bibinfo{year}{2011}).

\bibitem{Schwartz2017Aug}
\bibinfo{author}{Schwartz, R.~M.}, \bibinfo{author}{Gillezeau, C.~N.},
  \bibinfo{author}{Liu, B.}, \bibinfo{author}{Lieberman-Cribbin, W.} \&
  \bibinfo{author}{Taioli, E.}
\newblock \bibinfo{journal}{\bibinfo{title}{{Longitudinal Impact of Hurricane
  Sandy Exposure on Mental Health Symptoms}}}.
\newblock {\emph{\JournalTitle{Int. J. Environ. Res. Public Health}}}
  \textbf{\bibinfo{volume}{14}}, \bibinfo{pages}{957},
  \doiprefix\url{10.3390/ijerph14090957} (\bibinfo{year}{2017}).

\bibitem{baylis_weather_2018}
\bibinfo{author}{Baylis, P.} \emph{et~al.}
\newblock \bibinfo{journal}{\bibinfo{title}{Weather impacts expressed
  sentiment}}.
\newblock {\emph{\JournalTitle{PLOS One}}} \textbf{\bibinfo{volume}{13}},
  \bibinfo{pages}{e0195750}, \doiprefix\url{10.1371/journal.pone.0195750}
  (\bibinfo{year}{2018}).

\bibitem{Mullins2019Dec}
\bibinfo{author}{Mullins, J.~T.} \& \bibinfo{author}{White, C.}
\newblock \bibinfo{journal}{\bibinfo{title}{{Temperature and mental health:
  Evidence from the spectrum of mental health outcomes}}}.
\newblock {\emph{\JournalTitle{J. Health Econ.}}}
  \textbf{\bibinfo{volume}{68}}, \bibinfo{pages}{102240},
  \doiprefix\url{10.1016/j.jhealeco.2019.102240} (\bibinfo{year}{2019}).

\bibitem{Obradovich2018Oct}
\bibinfo{author}{Obradovich, N.}, \bibinfo{author}{Migliorini, R.},
  \bibinfo{author}{Paulus, M.~P.} \& \bibinfo{author}{Rahwan, I.}
\newblock \bibinfo{journal}{\bibinfo{title}{{Empirical evidence of mental
  health risks posed by climate change}}}.
\newblock {\emph{\JournalTitle{Proc. Natl. Acad. Sci. U.S.A.}}}
  \textbf{\bibinfo{volume}{115}}, \bibinfo{pages}{10953--10958},
  \doiprefix\url{10.1073/pnas.1801528115} (\bibinfo{year}{2018}).

\bibitem{allen2019technical}
\bibinfo{author}{Allen, M.} \emph{et~al.}
\newblock \bibinfo{title}{Technical summary: Global warming of 1.5° c. an ipcc
  special report on the impacts of global warming of 1.5° c above
  pre-industrial levels and related global greenhouse gas emission pathways, in
  the context of strengthening the global response to the threat of climate
  change, sustainable development, and efforts to eradicate poverty}
  (\bibinfo{year}{2019}).

\bibitem{Palinkas2020Apr}
\bibinfo{author}{Palinkas, L.~A.} \& \bibinfo{author}{Wong, M.}
\newblock \bibinfo{journal}{\bibinfo{title}{{Global climate change and mental
  health}}}.
\newblock {\emph{\JournalTitle{Current Opinion in Psychology}}}
  \textbf{\bibinfo{volume}{32}}, \bibinfo{pages}{12--16},
  \doiprefix\url{10.1016/j.copsyc.2019.06.023} (\bibinfo{year}{2020}).

\bibitem{Lohmus2018Jul}
\bibinfo{author}{L{\ifmmode\tilde{o}\else\~{o}\fi}hmus, M.}
\newblock \bibinfo{journal}{\bibinfo{title}{{Possible Biological Mechanisms
  Linking Mental Health and Heat{\ifmmode---\else\textemdash\fi}A Contemplative
  Review}}}.
\newblock {\emph{\JournalTitle{Int. J. Environ. Res. Public Health}}}
  \textbf{\bibinfo{volume}{15}}, \bibinfo{pages}{1515},
  \doiprefix\url{10.3390/ijerph15071515} (\bibinfo{year}{2018}).

\bibitem{Berry2007}
\bibinfo{author}{Berry, H.~L.}
\newblock \bibinfo{journal}{\bibinfo{title}{'crowded suburbs' and 'killer
  cities': a brief review of the relationship between urban environments and
  mental health}}.
\newblock {\emph{\JournalTitle{N S W Public Health Bull}}}
  \textbf{\bibinfo{volume}{18}}, \bibinfo{pages}{222--7},
  \doiprefix\url{10.1071/nb07024} (\bibinfo{year}{2007}).

\bibitem{Burke2015Nov}
\bibinfo{author}{Burke, M.}, \bibinfo{author}{Hsiang, S.~M.} \&
  \bibinfo{author}{Miguel, E.}
\newblock \bibinfo{journal}{\bibinfo{title}{{Global non-linear effect of
  temperature on economic production}}}.
\newblock {\emph{\JournalTitle{Nature}}} \textbf{\bibinfo{volume}{527}},
  \bibinfo{pages}{235--239}, \doiprefix\url{10.1038/nature15725}
  (\bibinfo{year}{2015}).

\bibitem{Burke2018Aug}
\bibinfo{author}{Burke, M.} \emph{et~al.}
\newblock \bibinfo{journal}{\bibinfo{title}{{Higher temperatures increase
  suicide rates in the United States and Mexico}}}.
\newblock {\emph{\JournalTitle{Nat. Clim. Change}}}
  \textbf{\bibinfo{volume}{8}}, \bibinfo{pages}{723--729},
  \doiprefix\url{10.1038/s41558-018-0222-x} (\bibinfo{year}{2018}).

\bibitem{Dixon2007May}
\bibinfo{author}{Dixon, P.~G.} \emph{et~al.}
\newblock \bibinfo{journal}{\bibinfo{title}{{Effects of temperature variation
  on suicide in five U.S. counties, 1991{\textendash}2001}}}.
\newblock {\emph{\JournalTitle{Int. J. Biometeorol.}}}
  \textbf{\bibinfo{volume}{51}}, \bibinfo{pages}{395--403},
  \doiprefix\url{10.1007/s00484-006-0081-4} (\bibinfo{year}{2007}).

\bibitem{Qi2014Dec}
\bibinfo{author}{Qi, X.}, \bibinfo{author}{Hu, W.}, \bibinfo{author}{Mengersen,
  K.} \& \bibinfo{author}{Tong, S.}
\newblock \bibinfo{journal}{\bibinfo{title}{{Socio-environmental drivers and
  suicide in Australia: Bayesian spatial analysis}}}.
\newblock {\emph{\JournalTitle{BMC Public Health}}}
  \textbf{\bibinfo{volume}{14}}, \bibinfo{pages}{1--10},
  \doiprefix\url{10.1186/1471-2458-14-681} (\bibinfo{year}{2014}).

\bibitem{Likhvar2011Jan}
\bibinfo{author}{Likhvar, V.}, \bibinfo{author}{Honda, Y.} \&
  \bibinfo{author}{Ono, M.}
\newblock \bibinfo{journal}{\bibinfo{title}{{Relation between temperature and
  suicide mortality in Japan in the presence of other confounding factors using
  time-series analysis with a semiparametric approach}}}.
\newblock {\emph{\JournalTitle{Environ. Health Preventive Med.}}}
  \textbf{\bibinfo{volume}{16}}, \bibinfo{pages}{36--43},
  \doiprefix\url{10.1007/s12199-010-0163-0} (\bibinfo{year}{2011}).

\bibitem{Lee2007Jan}
\bibinfo{author}{Lee, H.-C.}, \bibinfo{author}{Tsai, S.-Y.} \&
  \bibinfo{author}{Lin, H.-C.}
\newblock \bibinfo{journal}{\bibinfo{title}{{Seasonal variations in bipolar
  disorder admissions and the association with climate: A population-based
  study}}}.
\newblock {\emph{\JournalTitle{J. Affect. Disord.}}}
  \textbf{\bibinfo{volume}{97}}, \bibinfo{pages}{61--69},
  \doiprefix\url{10.1016/j.jad.2006.06.026} (\bibinfo{year}{2007}).

\bibitem{Sung2013Feb}
\bibinfo{author}{Sung, T.-I.}, \bibinfo{author}{Chen, M.-J.} \&
  \bibinfo{author}{Su, H.-J.}
\newblock \bibinfo{journal}{\bibinfo{title}{{A positive relationship between
  ambient temperature and bipolar disorder identified using a national cohort
  of psychiatric inpatients}}}.
\newblock {\emph{\JournalTitle{Soc. Psychiatry Psychiatr. Epidemiol.}}}
  \textbf{\bibinfo{volume}{48}}, \bibinfo{pages}{295--302},
  \doiprefix\url{10.1007/s00127-012-0542-5} (\bibinfo{year}{2013}).

\bibitem{Hansen2008Oct}
\bibinfo{author}{Hansen, A.} \emph{et~al.}
\newblock \bibinfo{journal}{\bibinfo{title}{{The Effect of Heat Waves on Mental
  Health in a Temperate Australian City}}}.
\newblock {\emph{\JournalTitle{Environ. Health Perspect.}}}
  (\bibinfo{year}{2008}).

\bibitem{Obradovich2017May}
\bibinfo{author}{Obradovich, N.}, \bibinfo{author}{Migliorini, R.},
  \bibinfo{author}{Mednick, S.~C.} \& \bibinfo{author}{Fowler, J.~H.}
\newblock \bibinfo{journal}{\bibinfo{title}{{Nighttime temperature and human
  sleep loss in a changing climate}}}.
\newblock {\emph{\JournalTitle{Sci. Adv.}}} \textbf{\bibinfo{volume}{3}},
  \bibinfo{pages}{e1601555}, \doiprefix\url{10.1126/sciadv.1601555}
  (\bibinfo{year}{2017}).

\bibitem{Gubernot2014Oct}
\bibinfo{author}{Gubernot, D.~M.}, \bibinfo{author}{Anderson, G.~B.} \&
  \bibinfo{author}{Hunting, K.~L.}
\newblock \bibinfo{journal}{\bibinfo{title}{{The epidemiology of occupational
  heat exposure in the United States: a review of the literature and assessment
  of research needs in a changing climate}}}.
\newblock {\emph{\JournalTitle{Int. J. Biometeorol.}}}
  \textbf{\bibinfo{volume}{58}}, \bibinfo{pages}{1779--1788},
  \doiprefix\url{10.1007/s00484-013-0752-x} (\bibinfo{year}{2014}).

\bibitem{Karner2015Dec}
\bibinfo{author}{Karner, A.}, \bibinfo{author}{Hondula, D.~M.} \&
  \bibinfo{author}{Vanos, J.~K.}
\newblock \bibinfo{journal}{\bibinfo{title}{{Heat exposure during non-motorized
  travel: Implications for transportation policy under climate change}}}.
\newblock {\emph{\JournalTitle{Journal of Transport {\&} Health}}}
  \textbf{\bibinfo{volume}{2}}, \bibinfo{pages}{451--459},
  \doiprefix\url{10.1016/j.jth.2015.10.001} (\bibinfo{year}{2015}).

\bibitem{Samuelson2020Jun}
\bibinfo{author}{Samuelson, H.} \emph{et~al.}
\newblock \bibinfo{journal}{\bibinfo{title}{{Housing as a critical determinant
  of heat vulnerability and health}}}.
\newblock {\emph{\JournalTitle{Sci. Total Environ.}}}
  \textbf{\bibinfo{volume}{720}}, \bibinfo{pages}{137296},
  \doiprefix\url{10.1016/j.scitotenv.2020.137296} (\bibinfo{year}{2020}).

\bibitem{Kang2016}
\bibinfo{author}{Kang, S.~K.}, \bibinfo{author}{DeCelles, K.~A.},
  \bibinfo{author}{Tilcsik, A.} \& \bibinfo{author}{Jun, S.}
\newblock \bibinfo{journal}{\bibinfo{title}{{Whitened
  R{\ifmmode\acute{e}\else\'{e}\fi}sum{\ifmmode\acute{e}\else\'{e}\fi}s: Race
  and Self-Presentation in the Labor Market}}}.
\newblock {\emph{\JournalTitle{Adm. Sci. Q.}}} \textbf{\bibinfo{volume}{61}},
  \bibinfo{pages}{469--502}, \doiprefix\url{10.1177/0001839216639577}
  (\bibinfo{year}{2016}).

\bibitem{Penner2008}
\bibinfo{author}{Penner, A.~M.}
\newblock \bibinfo{journal}{\bibinfo{title}{{Race and Gender Differences in
  Wages: The Role of Occupational Sorting at the Point of Hire}}}.
\newblock {\emph{\JournalTitle{Sociological Quarterly}}}
  \textbf{\bibinfo{volume}{49}}, \bibinfo{pages}{597--614},
  \doiprefix\url{10.1111/j.1533-8525.2008.00129.x} (\bibinfo{year}{2008}).

\bibitem{Desmond2015}
\bibinfo{author}{Desmond, M.} \& \bibinfo{author}{Shollenberger, T.}
\newblock \bibinfo{journal}{\bibinfo{title}{{Forced Displacement From Rental
  Housing: Prevalence and Neighborhood Consequences}}}.
\newblock {\emph{\JournalTitle{Demography}}} \textbf{\bibinfo{volume}{52}},
  \bibinfo{pages}{1751--1772}, \doiprefix\url{10.1007/s13524-015-0419-9}
  (\bibinfo{year}{2015}).

\bibitem{Akbar2019}
\bibinfo{author}{Akbar, P.~A.}, \bibinfo{author}{Li, S.},
  \bibinfo{author}{Shertzer, A.} \& \bibinfo{author}{Walsh, R.~P.}
\newblock \bibinfo{journal}{\bibinfo{title}{{Racial Segregation in Housing
  Markets and the Erosion of Black Wealth}}}.
\newblock {\emph{\JournalTitle{NBER}}} \doiprefix\url{10.3386/w25805}
  (\bibinfo{year}{2019}).

\bibitem{Banzhaf2019}
\bibinfo{author}{Banzhaf, S.}, \bibinfo{author}{Ma, L.} \&
  \bibinfo{author}{Timmins, C.}
\newblock \bibinfo{journal}{\bibinfo{title}{{Environmental Justice: The
  Economics of Race, Place, and Pollution}}}.
\newblock {\emph{\JournalTitle{J. Econ. Perspect.}}}
  \textbf{\bibinfo{volume}{33}}, \bibinfo{pages}{185--208},
  \doiprefix\url{10.1257/jep.33.1.185} (\bibinfo{year}{2019}).

\bibitem{Belanger2015Mar}
\bibinfo{author}{B{\ifmmode\acute{e}\else\'{e}\fi}langer, D.},
  \bibinfo{author}{Gosselin, P.}, \bibinfo{author}{Valois, P.} \&
  \bibinfo{author}{Abdous, B.}
\newblock \bibinfo{journal}{\bibinfo{title}{{Neighbourhood and dwelling
  characteristics associated with the self-reported adverse health effects of
  heat in most deprived urban areas: A cross-sectional study in 9 cities}}}.
\newblock {\emph{\JournalTitle{Health {\&} Place}}}
  \textbf{\bibinfo{volume}{32}}, \bibinfo{pages}{8--18},
  \doiprefix\url{10.1016/j.healthplace.2014.12.014} (\bibinfo{year}{2015}).

\bibitem{Uejio2011Mar}
\bibinfo{author}{Uejio, C.~K.} \emph{et~al.}
\newblock \bibinfo{journal}{\bibinfo{title}{{Intra-urban societal vulnerability
  to extreme heat: The role of heat exposure and the built environment,
  socioeconomics, and neighborhood stability}}}.
\newblock {\emph{\JournalTitle{Health {\&} Place}}}
  \textbf{\bibinfo{volume}{17}}, \bibinfo{pages}{498--507},
  \doiprefix\url{10.1016/j.healthplace.2010.12.005} (\bibinfo{year}{2011}).

\bibitem{ferre2019hurricane}
\bibinfo{author}{Ferr{\'e}, I.~M.} \emph{et~al.}
\newblock \bibinfo{journal}{\bibinfo{title}{Hurricane maria’s impact on punta
  santiago, puerto rico: community needs and mental health assessment six
  months postimpact}}.
\newblock {\emph{\JournalTitle{Disaster Med Public Health Prep}}}
  \textbf{\bibinfo{volume}{13}}, \bibinfo{pages}{18--23}
  (\bibinfo{year}{2019}).

\bibitem{Gruebner2015Jun}
\bibinfo{author}{Gruebner, O.}, \bibinfo{author}{Lowe, S.~R.},
  \bibinfo{author}{Sampson, L.} \& \bibinfo{author}{Galea, S.}
\newblock \bibinfo{journal}{\bibinfo{title}{{The geography of post-disaster
  mental health: spatial patterning of psychological vulnerability and
  resilience factors in New York City after Hurricane Sandy}}}.
\newblock {\emph{\JournalTitle{Int. J. Health Geographics}}}
  \textbf{\bibinfo{volume}{14}}, \bibinfo{pages}{16--13},
  \doiprefix\url{10.1186/s12942-015-0008-6} (\bibinfo{year}{2015}).

\bibitem{Edo-Osagie2020Jul}
\bibinfo{author}{Edo-Osagie, O.}, \bibinfo{author}{De~La~Iglesia, B.},
  \bibinfo{author}{Lake, I.} \& \bibinfo{author}{Edeghere, O.}
\newblock \bibinfo{journal}{\bibinfo{title}{{A scoping review of the use of
  Twitter for public health research}}}.
\newblock {\emph{\JournalTitle{Comput. Biol. Med.}}}
  \textbf{\bibinfo{volume}{122}}, \bibinfo{pages}{103770},
  \doiprefix\url{10.1016/j.compbiomed.2020.103770} (\bibinfo{year}{2020}).

\bibitem{Sinnenberg2016Dec}
\bibinfo{author}{Sinnenberg, L.} \emph{et~al.}
\newblock \bibinfo{journal}{\bibinfo{title}{{Twitter as a Tool for Health
  Research: A Systematic Review}}}.
\newblock {\emph{\JournalTitle{American Public Health Association (APHA)
  publications}}}  (\bibinfo{year}{2016}).

\bibitem{Reece2017Oct}
\bibinfo{author}{Reece, A.~G.} \emph{et~al.}
\newblock \bibinfo{journal}{\bibinfo{title}{{Forecasting the onset and course
  of mental illness with Twitter data}}}.
\newblock {\emph{\JournalTitle{Sci. Rep.}}} \textbf{\bibinfo{volume}{7}},
  \bibinfo{pages}{1--11}, \doiprefix\url{10.1038/s41598-017-12961-9}
  (\bibinfo{year}{2017}).

\bibitem{Eichstaedt2018Oct}
\bibinfo{author}{Eichstaedt, J.~C.} \emph{et~al.}
\newblock \bibinfo{journal}{\bibinfo{title}{{Facebook language predicts
  depression in medical records}}}.
\newblock {\emph{\JournalTitle{Proc. Natl. Acad. Sci. U.S.A.}}}
  \textbf{\bibinfo{volume}{115}}, \bibinfo{pages}{11203--11208},
  \doiprefix\url{10.1073/pnas.1802331115} (\bibinfo{year}{2018}).

\bibitem{Kolliakou2020Feb}
\bibinfo{author}{Kolliakou, A.} \emph{et~al.}
\newblock \bibinfo{journal}{\bibinfo{title}{{Mental health-related
  conversations on social media and crisis episodes: a time-series regression
  analysis}}}.
\newblock {\emph{\JournalTitle{Sci. Rep.}}} \textbf{\bibinfo{volume}{10}},
  \bibinfo{pages}{1--7}, \doiprefix\url{10.1038/s41598-020-57835-9}
  (\bibinfo{year}{2020}).

\bibitem{Mitchell2013May}
\bibinfo{author}{Mitchell, L.}, \bibinfo{author}{Frank, M.~R.},
  \bibinfo{author}{Harris, K.~D.}, \bibinfo{author}{Dodds, P.~S.} \&
  \bibinfo{author}{Danforth, C.~M.}
\newblock \bibinfo{journal}{\bibinfo{title}{{The Geography of Happiness:
  Connecting Twitter Sentiment and Expression, Demographics, and Objective
  Characteristics of Place}}}.
\newblock {\emph{\JournalTitle{PLOS One}}} \textbf{\bibinfo{volume}{8}},
  \bibinfo{pages}{e64417}, \doiprefix\url{10.1371/journal.pone.0064417}
  (\bibinfo{year}{2013}).

\bibitem{Dodds2011}
\bibinfo{author}{Dodds, P.~S.}, \bibinfo{author}{Harris, K.~D.},
  \bibinfo{author}{Kloumann, I.~M.}, \bibinfo{author}{Bliss, C.~A.} \&
  \bibinfo{author}{Danforth, C.~M.}
\newblock \bibinfo{journal}{\bibinfo{title}{{Temporal Patterns of Happiness and
  Information in a Global Social Network: Hedonometrics and Twitter}}}.
\newblock {\emph{\JournalTitle{PLoS One}}} \textbf{\bibinfo{volume}{6}},
  \bibinfo{pages}{e26752}, \doiprefix\url{10.1371/journal.pone.0026752}
  (\bibinfo{year}{2011}).

\bibitem{budd2008wet}
\bibinfo{author}{Budd, G.~M.}
\newblock \bibinfo{journal}{\bibinfo{title}{Wet-bulb globe temperature
  (wbgt)—its history and its limitations}}.
\newblock {\emph{\JournalTitle{Journal of Science and Medicine in Sport}}}
  \textbf{\bibinfo{volume}{11}}, \bibinfo{pages}{20--32}
  (\bibinfo{year}{2008}).

\bibitem{CDC2021}
\bibinfo{author}{for Disease Control Wide-ranging ONline Data~for Epidemiologic
  Research (CDC~WONDER), C.}
\newblock \bibinfo{title}{Underlying cause of death} (\bibinfo{year}{2021}).

\bibitem{Lieberman-Cribbin2017}
\bibinfo{author}{Lieberman-Cribbin, W.}, \bibinfo{author}{Liu, B.},
  \bibinfo{author}{Schneider, S.}, \bibinfo{author}{Schwartz, R.} \&
  \bibinfo{author}{Taioli, E.}
\newblock \bibinfo{journal}{\bibinfo{title}{{Self-Reported and FEMA Flood
  Exposure Assessment after Hurricane Sandy: Association with Mental Health
  Outcomes}}}.
\newblock {\emph{\JournalTitle{PLOS One}}} \textbf{\bibinfo{volume}{12}},
  \bibinfo{pages}{e0170965}, \doiprefix\url{10.1371/journal.pone.0170965}
  (\bibinfo{year}{2017}).

\bibitem{Hoffman2020}
\bibinfo{author}{Hoffman, J.~S.}, \bibinfo{author}{Shandas, V.} \&
  \bibinfo{author}{Pendleton, N.}
\newblock \bibinfo{journal}{\bibinfo{title}{{The Effects of Historical Housing
  Policies on Resident Exposure to Intra-Urban Heat: A Study of 108 US Urban
  Areas}}}.
\newblock {\emph{\JournalTitle{Climate}}} \textbf{\bibinfo{volume}{8}},
  \bibinfo{pages}{12}, \doiprefix\url{10.3390/cli8010012}
  (\bibinfo{year}{2020}).

\bibitem{Locke2021}
\bibinfo{author}{Locke, D.~H.} \emph{et~al.}
\newblock \bibinfo{journal}{\bibinfo{title}{{Residential housing segregation
  and urban tree canopy in 37 US Cities}}}.
\newblock {\emph{\JournalTitle{npj Urban Sustain.}}}
  \textbf{\bibinfo{volume}{1}}, \bibinfo{pages}{1--9},
  \doiprefix\url{10.1038/s42949-021-00022-0} (\bibinfo{year}{2021}).

\bibitem{Tong2021}
\bibinfo{author}{Tong, K.} \emph{et~al.}
\newblock \bibinfo{journal}{\bibinfo{title}{{Measuring social equity in urban
  energy use and interventions using fine-scale data}}}.
\newblock {\emph{\JournalTitle{Proc. Natl. Acad. Sci. U.S.A.}}}
  \textbf{\bibinfo{volume}{118}}, \bibinfo{pages}{e2023554118},
  \doiprefix\url{10.1073/pnas.2023554118} (\bibinfo{year}{2021}).

\bibitem{Raymond2020May}
\bibinfo{author}{Raymond, C.}, \bibinfo{author}{Matthews, T.} \&
  \bibinfo{author}{Horton, R.~M.}
\newblock \bibinfo{journal}{\bibinfo{title}{{The emergence of heat and humidity
  too severe for human tolerance}}}.
\newblock {\emph{\JournalTitle{Sci. Adv.}}} \textbf{\bibinfo{volume}{6}},
  \bibinfo{pages}{eaaw1838}, \doiprefix\url{10.1126/sciadv.aaw1838}
  (\bibinfo{year}{2020}).

\bibitem{Harrington2020Sep}
\bibinfo{author}{Harrington, L.~J.} \& \bibinfo{author}{Otto, F. E.~L.}
\newblock \bibinfo{journal}{\bibinfo{title}{{Reconciling theory with the
  reality of African heatwaves}}}.
\newblock {\emph{\JournalTitle{Nat. Clim. Change}}}
  \textbf{\bibinfo{volume}{10}}, \bibinfo{pages}{796--798},
  \doiprefix\url{10.1038/s41558-020-0851-8} (\bibinfo{year}{2020}).

\bibitem{Biardeau2020Jan}
\bibinfo{author}{Biardeau, L.~T.}, \bibinfo{author}{Davis, L.~W.},
  \bibinfo{author}{Gertler, P.} \& \bibinfo{author}{Wolfram, C.}
\newblock \bibinfo{journal}{\bibinfo{title}{{Heat exposure and global air
  conditioning}}}.
\newblock {\emph{\JournalTitle{Nat. Sustainability}}}
  \textbf{\bibinfo{volume}{3}}, \bibinfo{pages}{25--28},
  \doiprefix\url{10.1038/s41893-019-0441-9} (\bibinfo{year}{2020}).

\bibitem{Pew2020Sep}
\bibinfo{title}{{10 facts about Americans and Twitter}} (\bibinfo{year}{2020}).
\newblock \bibinfo{note}{[Online; accessed 1. May 2021]}.

\bibitem{bullard2012wrong}
\bibinfo{author}{Bullard, R.~D.} \& \bibinfo{author}{Wright, B.}
\newblock \emph{\bibinfo{title}{The wrong complexion for protection: How the
  government response to disaster endangers African American communities}}
  (\bibinfo{publisher}{NYU Press}, \bibinfo{year}{2012}).

\bibitem{hutto2014vader}
\bibinfo{author}{Hutto, C.} \& \bibinfo{author}{Gilbert, E.}
\newblock \bibinfo{title}{Vader: A parsimonious rule-based model for sentiment
  analysis of social media text}.
\newblock In \emph{\bibinfo{booktitle}{Proceedings of the International AAAI
  Conference on Web and Social Media}}, vol.~\bibinfo{volume}{8}
  (\bibinfo{year}{2014}).

\bibitem{gilbert_vader_2014}
\bibinfo{author}{Gilbert, C. H.~E.} \& \bibinfo{author}{Hutto, E.}
\newblock \bibinfo{title}{Vader: {A} parsimonious rule-based model for
  sentiment analysis of social media text}.
\newblock In \emph{\bibinfo{booktitle}{Eighth {International} {Conference} on
  {Weblogs} and {Social} {Media} ({ICWSM}-14). {Available} at (20/04/16)
  http://comp. social. gatech. edu/papers/icwsm14. vader. hutto. pdf}},
  vol.~\bibinfo{volume}{81}, \bibinfo{pages}{82} (\bibinfo{year}{2014}).

\bibitem{xia_continental-scale_2012}
\bibinfo{author}{Xia, Y.} \emph{et~al.}
\newblock \bibinfo{journal}{\bibinfo{title}{Continental-scale water and energy
  flux analysis and validation for the {North} {American} {Land} {Data}
  {Assimilation} {System} project phase 2 ({NLDAS}-2): 1. {Intercomparison} and
  application of model products}}.
\newblock {\emph{\JournalTitle{Journal of Geophysical Research: Atmospheres}}}
  \textbf{\bibinfo{volume}{117}},
  \doiprefix\url{https://doi.org/10.1029/2011JD016048} (\bibinfo{year}{2012}).
\newblock \bibinfo{note}{\_eprint:
  https://agupubs.onlinelibrary.wiley.com/doi/pdf/10.1029/2011JD016048}.

\bibitem{rao2020projections}
\bibinfo{author}{Rao, K.~K.} \emph{et~al.}
\newblock \bibinfo{journal}{\bibinfo{title}{projections of heat stress and
  associated work performance over india in response to global warming}}.
\newblock {\emph{\JournalTitle{Scientific reports}}}
  \textbf{\bibinfo{volume}{10}}, \bibinfo{pages}{1--14} (\bibinfo{year}{2020}).

\bibitem{hu2017impact}
\bibinfo{author}{Hu, X.}, \bibinfo{author}{Wu, J.}, \bibinfo{author}{Chen, P.},
  \bibinfo{author}{Sun, T.} \& \bibinfo{author}{Li, D.}
\newblock \bibinfo{journal}{\bibinfo{title}{Impact of climate variability and
  change on crime rates in tangshan, china}}.
\newblock {\emph{\JournalTitle{Science of the total environment}}}
  \textbf{\bibinfo{volume}{609}}, \bibinfo{pages}{1041--1048}
  (\bibinfo{year}{2017}).

\bibitem{chien2016spatiotemporal}
\bibinfo{author}{Chien, L.-C.}, \bibinfo{author}{Guo, Y.} \&
  \bibinfo{author}{Zhang, K.}
\newblock \bibinfo{journal}{\bibinfo{title}{Spatiotemporal analysis of heat and
  heat wave effects on elderly mortality in texas, 2006--2011}}.
\newblock {\emph{\JournalTitle{Science of the Total Environment}}}
  \textbf{\bibinfo{volume}{562}}, \bibinfo{pages}{845--851}
  (\bibinfo{year}{2016}).

\bibitem{armstrong2019role}
\bibinfo{author}{Armstrong, B.} \emph{et~al.}
\newblock \bibinfo{journal}{\bibinfo{title}{The role of humidity in
  associations of high temperature with mortality: a multicountry, multicity
  study}}.
\newblock {\emph{\JournalTitle{Environmental health perspectives}}}
  \textbf{\bibinfo{volume}{127}}, \bibinfo{pages}{097007}
  (\bibinfo{year}{2019}).

\bibitem{vida2012relationship}
\bibinfo{author}{Vida, S.}, \bibinfo{author}{Durocher, M.},
  \bibinfo{author}{Ouarda, T.~B.} \& \bibinfo{author}{Gosselin, P.}
\newblock \bibinfo{journal}{\bibinfo{title}{Relationship between ambient
  temperature and humidity and visits to mental health emergency departments in
  qu{\'e}bec}}.
\newblock {\emph{\JournalTitle{Psychiatric Services}}}
  \textbf{\bibinfo{volume}{63}}, \bibinfo{pages}{1150--1153}
  (\bibinfo{year}{2012}).

\bibitem{ding2016importance}
\bibinfo{author}{Ding, N.}, \bibinfo{author}{Berry, H.~L.} \&
  \bibinfo{author}{Bennett, C.~M.}
\newblock \bibinfo{journal}{\bibinfo{title}{The importance of humidity in the
  relationship between heat and population mental health: evidence from
  australia}}.
\newblock {\emph{\JournalTitle{PLOS One}}} \textbf{\bibinfo{volume}{11}},
  \bibinfo{pages}{e0164190} (\bibinfo{year}{2016}).
